Testing Statistical Graphics

### 2022-06-27 index.qmd
I really hate writing conclusions.

# Conclusion

>>>>

# Conclusion
Testing features of visualization graphically using online platforms provides an incredibly powerful and efficient way to establish empirical guidelines for statistical graphics and visualization. There are nearly endless ways to combine web graphics, user interactions, and data collection to get insight into perception and use of graphics in practical settings. We have been continually surprised at the richness of the data collected in these experiments and the ability to combine qualitative and quantitative assessment to support conclusions that are both nuanced and of practical use when deciding how to design and present data using visualizations.
